Numerical Solution of Point Defect Equations by MOOSE

### 2021-01-04 examples/point_defects/article/article.tex
article-edit

        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zi_scaled}}

@@

        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zv_scaled}}

@@

        \subfloat{\includegraphics[scale=0.55]{sink_strength_ki_scaled}}

@@

        \subfloat{\includegraphics[scale=0.55]{sink_strength_kv_scaled}}
        \caption{Total GB Sink Strengths for high dose rate neutron irradation}

@@

        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Z_scaled}}

@@

        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_k_scaled}}

@@

% In nano-scale case, since the domain size is not big enough, the boundaries become
% closer to each other. This causes point defects to reach sinks before they react with each other
% and recombination plateau to disappear as it can be seen in Fig. 2. The nanoscale case acts like
% a high-sink and high-temp condition case despite its low-sink and low-temperature. Therefore,
% change in production bias does not have a significant effect on average concentration behavior
% in nanoscale
%
% On the other hand, in micro-scale case, the domain has reasonable size, and thus
% boundaries are far from each other. This provides defects more time to accumulate inside the
% domain and recombine with each other after they reach a specific concentration. Figure 3
% clearly shows the effect of production bias on average concentration.
%
% Effect of production bias on spatial profile of defect concentrations for nanoscale is
% shown in Figure 4. The results seem not affected too much because of the same reasons
% mentioned previously for average concentration.
%
% The micro-scale results (Fig. 5) are quite interesting and worth to think over. The
% concentration profiles of interstitials for 0.1%, 5% and 10% cases are flipped over. A closer look
% at evolution of 5% case over time in Fig. 6, after the end of quasi-steady-state region (t=10 -4 s in
% Fig 3.), the average interstitial concentration starts to decrease as they segregate through sinks.
% At steady state, the average interstitial concentration becomes minimum at the center and
% maximum near boundaries because of segregation.
%
% The defect production rate (K 0 ) is the source term in point defect equations and has a
% significant effect on concentrations.
% In nano-scale case, the average concentration behavior is like high-sink density behavior
% because of narrow domain. But, when the defect production rate increases, the average
% concentration is shifted upward, and interstitial and vacancy average concentrations get closer
% to each other because the production compensates more absorption at sinks than previous.
% Based on this, if the production rate increased sufficiently, the recombination zone would
% appear again in nano-scale domain.

>>>>

        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron}}
        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron_500-5000nm}}

@@

        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron}}
        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron_500-5000nm}}

@@

        \subfloat{\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron}}
        \subfloat{\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron_500-5000nm}}

@@

        \subfloat{\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron}}
        \subfloat{\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron_500-5000nm}}
        \caption{Total GB Sink Strengths for low dose rate neutron irradation}

@@

        \subfloat{a)\includegraphics[scale=0.45]{sink_strength_moose_neutron_3D_Zi_scaled}}
        \subfloat{b)\includegraphics[scale=0.45]{sink_strength_moose_neutron_3D_Zv_scaled}}

@@

        \subfloat{c)\includegraphics[scale=0.45]{sink_strength_moose_neutron_3D_ki_scaled}}
        \subfloat{d)\includegraphics[scale=0.45]{sink_strength_moose_neutron_3D_kv_scaled}}

@@

% In nano-scale case, since the domain size is not big enough, the boundaries become
% closer to each other. This causes point defects to reach sinks before they react with each other
% and recombination plateau to disappear as it can be seen in Fig. 2. The nanoscale case acts like
% a high-sink and high-temp condition case despite its low-sink and low-temperature. Therefore,
% change in production bias does not have a significant effect on average concentration behavior
% in nanoscale
%
% On the other hand, in micro-scale case, the domain has reasonable size, and thus
% boundaries are far from each other. This provides defects more time to accumulate inside the
% domain and recombine with each other after they reach a specific concentration. Figure 3
% clearly shows the effect of production bias on average concentration.
%
% Effect of production bias on spatial profile of defect concentrations for nanoscale is
% shown in Figure 4. The results seem not affected too much because of the same reasons
% mentioned previously for average concentration.
%
% The micro-scale results (Fig. 5) are quite interesting and worth to think over. The
% concentration profiles of interstitials for 0.1%, 5% and 10% cases are flipped over. A closer look
% at evolution of 5% case over time in Fig. 6, after the end of quasi-steady-state region (t=10 -4 s in
% Fig 3.), the average interstitial concentration starts to decrease as they segregate through sinks.
% At steady state, the average interstitial concentration becomes minimum at the center and
% maximum near boundaries because of segregation.
%
% The defect production rate (K 0 ) is the source term in point defect equations and has a
% significant effect on concentrations.
% In nano-scale case, the average concentration behavior is like high-sink density behavior
% because of narrow domain. But, when the defect production rate increases, the average
% concentration is shifted upward, and interstitial and vacancy average concentrations get closer
% to each other because the production compensates more absorption at sinks than previous.
% Based on this, if the production rate increased sufficiently, the recombination zone would
% appear again in nano-scale domain.
\newpage
\section{Discussion} \hspace{10pt}
-Comparison of Neutron and Ion irradation.
